\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx}

\title{Personal Learning Goals}
\author{Ali Asghar Yousuf - ay06993}
\date{\today}

\begin{document}
\maketitle

\section*{Goals}
\begin{enumerate}
    \item Successfully complete the project.

          As someone with 0 (zero) experience with \texttt{MATLAB} and \textit{Robotics}
          in general, it would be a huge milestone for me to successfully complete this
          course and implement the project. I would also like to learn \texttt{MATLAB}
          and \texttt{Simulink} proficiently enough to implement a project all on my own.

    \item Simulate a robot in a 3D environment using ROS and Gazebo.

          I have learned the theoretical concepts of mobile robots and their kinematics
          in the course. We have also learned how to simulate a differential drive robot
          in a 2D environment using ROS and Gazebo. I would like to extend this knowledge
          to simulate a real robot in a 3D environment. This will help me understand the
          practical challenges of implementing a robot in a real world environment.

    \item Implement a path planning algorithm for the robot.

          I have studied a number of path planning algorithms and other optimization
          techniques in my undergraduate studies including BFS, DFS, Dijkstra's, A*, EA. I would like
          to implement couple of these algorithms in the project. This will help me
          understand the practical challenges of implementing a path planning algorithm
          in a real world environment.
\end{enumerate}

\end{document}