\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx}

\title{Revision and Assessment Plan}
\author{Ali Asghar Yousuf - ay06993}
\date{\today}

\begin{document}
\maketitle

\section*{Goals}
\subsection*{Successfully complete the project}
My first goal is essentially still the same as the one I had set in my personal
learning goals document. I would like to successfully complete the project. But
I would like to add some more details to this goal. In order to successfully
complete the project, I would need to first strengthen my theoretical knowledge
of mobile robots and their kinematics.

\subsubsection*{Assessment Plan}
I will assess my progress towards this goal by the number of hours I spend
studying the theoretical concepts of mobile robots using the course material
and other resources. I will also assess my progress by the number of hours I
spend implementing the project. And of course the outcome of the project will
be the ultimate assessment of my progress towards this goal.

\subsection*{Attain Technical Skills}
My second goal is an extension of the first one. I would like to learn all the
technical skills required to successfully complete the project, including
\texttt{MATLAB}, \texttt{Simulink}, \texttt{ROS} and \texttt{Gazebo}.

\subsubsection*{Assessment Plan}
The progress towards this goal will be assessed by the quality of the work I
produce using these tools. I will update a GitHub repository with all the code
I write for the project. I will also update a log with all the details of the
project including the challenges I face and how I overcome them. The quality of the code and the log will be the ultimate assessment
of my progress towards this goal.

\subsection*{Implement Path Coverage Algorithms}
After getting some clarity on the essentials of the project, I have slightly
updated my third goal. I would like to implement a path coverage algorithm
which is not only efficient but also robust enough to handle the real world
challenges.

\subsubsection*{Assessment Plan}
I will assess my progress towards this goal by the different path coverage
algorithms I test and implement. I will also assess my progress by the number
of hours I spend implementing these algorithms. The final assessment of my
progress towards this goal will be the quality of the algorithm I implement.

\end{document}